\thetitle

### 2017-12-31 TeX/manuscript.tex
additions to abstract and background

\begin{abstract}
    General artificial intelligence refers to machine intelligence than performs a task as successfully as a human does.

@@

>>>>

\begin{abstract}

\textcolor{red}{Rewritten abstract:}
	Contrary to the way Humans classify information, current neural networks exclusively process numerical (continuous) information. We propose an architecture for Deep Learning models that combine numerical and categorical information... \\

    General artificial intelligence refers to machine intelligence than performs a task as successfully as a human does.

@@

\subsection{Routing categorical information through the network}
